Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
DMGizing the list of tafaseer.

# 2 The Tafasir

@@

al-Bahr al-Muhit by Abu Hayyan
al-Jami' li Ahkam al-Qur'an by al-Qurtubi
al-Kashshaaf by al-Zamakhshari 
al-Muharrar al-Wajiz fi Tafsir al-Kitaab al-'Aziz by Ibn Atiyyah
Al-Nukat wal 'Uyuun by al-Mawardi
Anwar al-Tanzil wa Asrar al-Ta’wil by al-Baydawi
Bahr al-Uluum by al-Samarqandi
Jami` al-bayan `an Ta'wil 'ay al-Qur'an by al-Tabari
Lubab al-Ta'wil fi Ma'ani al-Tanzil by al-Khazin
Ma’alm al-Tanzil by al-Baghawi
Madarik al-Tanzil wa Haqa'iq al-Ta'wil by al-Nasafi
Mafatih al-Ghayb by al-Razi
Tafsir al-Jalalayn by al-Mahali and al-Suyuti
Tafsir al-Qur'an by al-Fairuzabadi
Tafsir al-Qur’an by Ibn Abd-al-Salam
Tafsir al-Qur'an al-Azim by Ibn Kathir
Zad al-Masir fi 'ilm al-Tafsir by Ibn al-Jawzi

>>>>

# 2 The Tafāsīr

@@

For reference, the following tafāsīr which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.

TODO: If anybody feels like properly capitalizing the titles again, I don't, rigt now. The uppercase letters can be looked up (and then copied and pasted) by clicking on the lowercase letters on https://en.wikipedia.org/wiki/DIN_31635. You could also try https://github.com/sixtyfive/de_dmg/blob/master/windows7810/de_dmg_amd64.msi if you have Windows, but it's quite old and I don't know if it'll still work (but it might).

* *al-baḥr al-muḥīt* by *Abū Ḥayyān*
* *al-ǧāmiʿ li-ʾaḥkām al-qurʾān* by *al-Qurṭubī*
* *al-kaššāf* by *az-Zamaḫšarī*
* *al-muḥarrar al-waǧīz fī tafsīr al-kitāb al-ʾazīz* by *Ibn ʿAṭīya*
* *an-nukat wa-l-ʿuyūn* by *al-Māwardī*
* *anwār at-tanzīl wa-ʾasrār at-taʾwīl* by *al-Bayḍāwī*
* *baḥr al-ʿulūm* by *as-Samarqandī*
* *ǧāmiʿ al-bayān fī tafsīr al-Qurʾān* by *aṭ-Ṭabarī*
* *lubāb at-taʾwīl fī maʿānī at-tanzīl* by *al-Ḫāzin*
* *maʿlam at-tanzīl* by *al-Baġawī*
* *madārik at-tanzīl wa-ḥaqa'iq at-taʾwīl* by *an-Nasafī*
* *mafātīḥ al-ġayb* by *ar-Rāzī*
* *tafsīr al-ǧalālayn* by *al-Maḥallī* and *as-Suyūṭī*
* *tafsīr al-qurʾān* by *al-Fayrūzābādī*
* *tafsīr al-qurʾān* by *Ibn ʿAbdi-s-Salām*
* *tafsīr al-qurʾān al-karīm* by *Ibn Kaṯīr*
* *zād al-masīr fī ʿilm at-tafsīr* by *Ibnu-l-Ǧawzī*
